Analyzing the influence of Selection on Genetic Programming's Generalization ability in Symbolic Regression

### 2022-06-26 docs/rmd/presentation/slides.Rmd

---
title: "Analyzing the influence of Selection on Genetic Programming's Generalization ability in Symbolic Regression"
subtitle: "A comparison of epsilon-lexicase Selection and Tournament Selection"
date: "2022-06-29"
output:
  beamer_presentation:
    colortheme: "beaver"
    fonttheme: "structurebold"
    keep_tex: true
    fig_caption: yes
    number_sections: true
    slide_level: 2
toc: yes
toc_depth: 1
bibliography: ../bib/bib/ref.bib
csl: ../bib/csl/harvard1.csl
---

@@

## Research Question

@@

* A metaheuristic that searches for computer programs that solve a given problem
* Evolutionary algorithm that simulates the process of Darwinian evolution:
  1. Fitnessfunction: Evaluates the quality of a solution
  1. Selection: Solutions are selected based on their individual fitness
  2. Variation: Mutation and recombination of solutions
* Unique Features:
  * Evolve solutions of variable length and structure
  * Solutions are typically represented by recursive tree structures

@@

@@

@@

# Theoretical Foundations

@@

# References

>>>>

---
title: "Analyzing the influence of Selection on Genetic Programming's Generalization ability in Symbolic Regression"
subtitle: "A comparison of epsilon-lexicase Selection and Tournament Selection"
date: "2022-06-29"
output:
  beamer_presentation:
    colortheme: "beaver"
    fonttheme: "structurebold"
    keep_tex: true
    fig_caption: yes
    number_sections: true
    slide_level: 2
toc: yes
toc_depth: 2
bibliography: ../bib/bib/ref.bib
csl: ../bib/csl/harvard1.csl
---

@@

# Research Question

@@

* A metaheuristic that searches for computer programs that solve a given problem
* Inventor: John R. Koza ^[@koza_main]
* Evolutionary algorithm that simulates the process of Darwinian evolution:
  1. Population based
  2. The quality of solutions is evaluated by a fitness function
  3. Selection: Solutions are selected based on their individual fitness
  4. Variation: Mutation and recombination of solutions
* Unique Features:
  * Evolve solutions of variable length and structure
  * Solutions are typically represented by recursive tree structures

@@

* Operator that selects individual solutions from the population for reproduction and mutation
* Most commonly used selection operator in GP: Tournament selection^[@10.1007/978-3-642-16493-4_19, p.181]
* Intuition: High chance for "generalist" solutions to be selected since it is based on aggregated fitness scores

## epsilon-Lexicase Selection

* Recent alternative: Lexicase Selection and it's variation $\epsilon$-lexicase selection
* Idea: Selection method for uncompromising, continous-valued symbolic regression problems ^[@6920034, p.12]
* Increases genetic diversity inside the population^[@6920034, p.1]
* Higher chance for "specialist" solutions to be selected since it is decided on a per case basis
* Performance increases have been demosntrated in many benchmarking problems ^[@epsilon_lexicase_main, p.744-745]

@@

* Task: Find a mathematical model that fits a given set of datapoints
* One of the first applications of Genetic Programming introduced by @koza_main
* GP, even though more time consuming, can

@@

@@

...
\newpage
